Analysis and figures

### 2025-02-07 Analysis.qmd
Updates to review summary sub-plot code

  ggplot() +
  geom_sf(data = countries_shp, colour = "gray90", fill = "gray80") +
  geom_sf(shape = 21, fill = "aquamarine4", colour = "white", alpha = 0.5, size = 3.5) +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
plot_studyAreaMap
ggsave(plot = plot_studyAreaMap, "Figures/StudiesMap.png")

@@

```{r Study area size}
#| fig-width: 7
#| fig-height: 4

@@

  ggplot() +
  geom_col(aes(x = Size, y = Articles),
           fill = "aquamarine4", colour = "white",
           width = 1, linewidth = 2) +
  labs(x = "", y = "") +
  scale_x_discrete(labels = c("< 1", "1 - 10", "10 - 10<sup>2</sup>",
                              "10<sup>2</sup> - 10<sup>3</sup>",
                              "10<sup>3</sup> - 10<sup>4</sup>",
                              "10<sup>4</sup> - 10<sup>5</sup>",
                              "10<sup>5</sup> - 10<sup>6</sup>",
                              "\\> 10<sup>6</sup>")) +
  theme(panel.grid = element_blank(),
        axis.text.x = element_markdown(size = 20, angle = 90,
                                       vjust = 0.5, hjust = 1),
        axis.text.y = element_blank(), axis.ticks = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA))
plot_studyAreaSize

ggsave("Figures/StudyAreaPlot.png",
       plot = plot_studyAreaSize, width = 7, height = 4, bg='transparent')
```

@@

  ggplot() +
  geom_col(aes(x = Articles, y = `Taxa keywords`, fill = Group),
           position = position_dodge2(reverse = TRUE), width = 0.8) +
  scale_fill_manual("", values = c("aquamarine4", "goldenrod2", "gray70")) +
  scale_x_continuous(expand = c(0,0)) +
  labs(x = "Articles", y = "") +
  theme(panel.grid = element_blank(),
        legend.text = element_text(size = 20), axis.text = element_text(size = 21),
        axis.title = element_text(size = 19), axis.ticks.y = element_blank(),
        panel.background = element_rect(fill='transparent', color = NA),
        plot.background = element_rect(fill='transparent', color = NA),
        legend.background = element_rect(fill = 'transparent', color = NA))
plot_focalTaxa

ggsave("Figures/TaxaPlot.png",
       plot_focalTaxa, width = 10, height = 4, bg='transparent')
```

@@

# Plot site quantity distribution
plot_siteQuantity <- sheet_DataCollection |>
  filter(`Site quantity` != "Unclear") |>
  mutate(`Site quantity` = as.numeric(`Site quantity`)) |>
  ggplot() +
  geom_histogram(aes(x = `Site quantity`),
                 binwidth = 0.25, fill = "aquamarine4", colour = "white",
                 linewidth = 2) +
  geom_vline(aes(xintercept = median(`Site quantity`, na.rm = TRUE)), 
             colour = "goldenrod2", linetype = 1, linewidth = 2) +
  scale_x_continuous(transform = "log10",
                     breaks = c(0, 10, 25, 50, 100, 250, 500,
                                1000, 2500, 5000, 7500),
                     expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0), position = "right") +
  labs(y = "Site\nquantity", x = "") +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        axis.text.x = element_text(size = 23, angle = 90,
                                   vjust = 0.5, hjust = 1),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.line.x = element_line(), 
        axis.title.y = element_text(size = 35, colour = "aquamarine4"))
plot_siteQuantity
ggsave(plot = plot_siteQuantity, filename = "Figures/Sites.png",
       height = 3, width = 12)

@@

  ggplot() +
  geom_histogram(aes(x = StudyMonths), 
                 binwidth = 0.2, fill = "aquamarine4", colour = "white",
                 linewidth = 2) +
  geom_vline(aes(xintercept = median(StudyMonths, na.rm = TRUE)), 
             colour = "goldenrod2", linetype = 1, linewidth = 2) +
  labs(x = "", y = "Study\nduration") +
  scale_x_continuous(transform = "log10",
                     breaks = c(1, 6, 12, 60, 
                                120, 240, 480), 
                     labels = c("1 month", "6 months", "1 year", "5 years", 
                                "10 years", "20 years", "40 years"),
                     expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0), position = "right") +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        axis.text.x = element_text(size = 23, angle = 90,
                                   vjust = 0.5, hjust = 1),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        axis.line.x = element_line(), 
        axis.title.y = element_text(size = 35, colour = "aquamarine4"))
plot_studyDuration
ggsave(plot = plot_studyDuration, filename = "Figures/Duration.png",
       height = 3.5, width = 12)

>>>>

  ggplot() +
  geom_sf(data = countries_shp, colour = "gray90", fill = "gray60", linewidth = 0.1) +
  geom_sf(shape = 23, 
          fill = "goldenrod2", colour = "white",
          size = 1.5) +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
plot_studyAreaMap

ggsave("Figures/StudiesMap.eps", plot = plot_studyAreaMap,
       width = 85, height = 50, units = "mm", bg = "transparent")

@@

```{r Study area size}
#| fig-width: "6.52cm"
#| fig-height: "3.7cm"

@@

  ggplot() +
  geom_col(aes(x = Size, y = Articles),
           fill = "#4D7668", colour = "white",
           width = 1, linewidth = .5) +
  labs(x = "", y = "") +
  scale_x_discrete(labels = c("< 1", "1 - 10", "10 - 10<sup>2</sup>",
                              "10<sup>2</sup> - 10<sup>3</sup>",
                              "10<sup>3</sup> - 10<sup>4</sup>",
                              "10<sup>4</sup> - 10<sup>5</sup>",
                              "10<sup>5</sup> - 10<sup>6</sup>",
                              "\\> 10<sup>6</sup>")) +
  theme(panel.grid = element_blank(),
        axis.text.x = element_markdown(size = 8, angle = 90,
                                       vjust = 0.5, hjust = 1,
                                       family = "Helvetica"),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA))
plot_studyAreaSize

ggsave("Figures/StudyAreaPlot.eps",
       plot = plot_studyAreaSize, 
       width = 80, height = 45, units = "mm",
       bg='transparent')
```

@@

  ggplot() +
  geom_col(aes(x = Articles, y = `Taxa keywords`, fill = Group),
           position = position_dodge2(reverse = TRUE), width = 0.8) +
  scale_fill_manual("", 
                    values = c("#4D7668", "goldenrod3", "gray40"),
                    limits = c("Overall", "Threatened", "Invasive"),
                    labels = c("Total", "Threatened", "Invasive")) +
  scale_x_continuous(expand = c(0,0), breaks = c(0, 15, 30, 45)) +
  labs(x = "Articles", y = "") +
  theme(#legend.position = "top",
        panel.grid = element_blank(),
        legend.text = element_text(size = 8, family = "Helvetica", colour = "#585858"),
        legend.title = element_text(size = 8, family = "Helvetica", colour = "#585858"),
        axis.text = element_text(size = 8, family = "Helvetica", colour = "#585858"),
        axis.title = element_text(size = 8, family = "Helvetica", colour = "#585858"), 
        axis.ticks.y = element_blank(),
        panel.background = element_rect(fill='transparent', color = NA),
        plot.background = element_rect(fill='transparent', color = NA),
        legend.background = element_rect(fill = 'transparent'),
        legend.key.size = unit(4, 'mm'),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0, -5, 0, 0),
        axis.line.x = element_line(colour = "#585858", linewidth = 0.3))
plot_focalTaxa

ggsave("Figures/TaxaPlot.eps",
       plot_focalTaxa, width = 90, height = 40, units = "mm",
       bg = "transparent")
```

@@

# Plot site quantity distribution
plot_siteQuantity <- sheet_DataCollection |>
  filter(`Site quantity` != "Unclear") |>
  mutate(`Site quantity` = as.numeric(`Site quantity`)) |>
  ggplot() +
  geom_histogram(aes(x = `Site quantity`),
                 bins = 12,
                 fill = "#4D7668", colour = "white",
                 linewidth = 0.5) +
  geom_vline(aes(xintercept = median(`Site quantity`, na.rm = TRUE)), 
             colour = "goldenrod2", linetype = 1, linewidth = 2) +
  scale_x_continuous(transform = "log10",
                     breaks = c(0, 10, 25, 50, 100, 250, 500,
                                1000, 2500, 5000, 7500),
                     expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0), position = "right") +
  labs(y = "Number of\nsites", x = "") +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill = 'transparent',
                                        color = NA),
        plot.background = element_rect(fill = 'transparent', 
                                       color = NA),
        axis.text.x = element_text(size = 8, angle = 60,
                                   #vjust = .5,
                                   hjust = 1,
                                   colour = "#585858",
                                   family = "Helvetica"),
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        plot.margin = margin(20,10,0,10),
        axis.line.x = element_line(colour = "#585858",
                                   linewidth = .1), 
        axis.title.y = element_text(size = 10, 
                                    colour = "#585858",
                                   family = "Helvetica"))
plot_siteQuantity
ggsave(plot = plot_siteQuantity, 
       filename = "Figures/Sites.eps",
       height = 35, width = 110, units = "mm")

@@

  ggplot() +
  geom_histogram(aes(x = StudyMonths), 
                 bins = 12,
                 fill = "#4D7668", colour = "white",
                 linewidth = 0.5) +
  geom_vline(aes(xintercept = median(StudyMonths, na.rm = TRUE)), 
             colour = "goldenrod2", linetype = 1, linewidth = 2) +
  labs(x = "", y = "Study\nduration") +
  scale_x_continuous(transform = "log10",
                     breaks = c(1, 6, 12, 60, 
                                120, 240, 480), 
                     labels = c("1 month", "6 months", "1 year", "5 years", 
                                "10 years", "20 years", "40 years"),
                     expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0), position = "right") +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill = 'transparent', 
                                        color = NA),
        plot.background = element_rect(fill = 'transparent',
                                       color = NA),
        axis.text.x = element_text(size = 8, angle = 60,
                                   hjust = 1, 
                                   family = "Helvetica",
                                   colour = "#585858"),
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(),
        axis.line.x = element_line(colour = "#585858",
                                   linewidth = .1), 
        axis.title.y = element_text(size = 10, 
                                    colour = "#585858",
                                    family = "Helvetica"),
        plot.margin = margin(20,10,0,10))
plot_studyDuration
ggsave(plot = plot_studyDuration, 
       filename = "Figures/Duration.eps",
       height = 35, width = 110, units = "mm",
       bg = "transparent")
